Legacy Data Confounds Genomics Studies

### 2019-07-12 LatexManuscript/legacy.tex
two comments

This method identifies a total of 24,390 variants associated to $Q$ distributed across the genome with 15,270 passing the 1kGP strict mask filter (Figures \ref{NRS_Manhattan},\ref{NRI_Manhattan}, \ref{RS_Manhattan}, and \ref{RI_Manhattan}). Most analyses below focus on the 15,270 variants satisfying the strict mask, since these variants are unlikely to be filtered by standard pipelines.
To account for the large number of tests, we used a two-stage Benjamini \& Hochberg step-up FDR-controlling procedure to adjust the p-values using a nominal Type-I error rate $\alpha = 0.01$ \citep{Benjamini2006}. 
We tested SNPs, INDELs and repetitive regions separately as they may have different error rates (Table \ref{sigTable}).
Lists of $Q$-associated variants and individuals with low $Q$ are provided in Supplementary Data.

>>>>

This method \sgcomment{GCAT?} identifies a total of 24,390 variants associated to $Q$ distributed across the genome with 15,270 passing the 1kGP strict mask filter (Figures \ref{NRS_Manhattan},\ref{NRI_Manhattan}, \ref{RS_Manhattan}, and \ref{RI_Manhattan}). Most analyses below focus on the 15,270 variants satisfying the strict mask, since these variants are unlikely to be filtered by standard pipelines.
To account for the large number of tests, we used a two-stage Benjamini \& Hochberg step-up FDR-controlling procedure to adjust the p-values using a nominal Type-I error rate $\alpha = 0.01$ \citep{Benjamini2006}. 
We tested SNPs, INDELs and repetitive regions separately as they may have different error rates (Table \ref{sigTable}).
Lists of $Q$-associated variants and individuals with low $Q$ are provided in Supplementary Data.
